Flat histogram method comparison on 2D Ising Model

### 2020-01-16 ising/ising.tex
fixed paper ising where to look for figs.
fixed where fac was looking for bib file.

\begin{figure}
\includegraphics[width=\columnwidth]{figs/ising/gamma-n32.pdf}
  \caption{
  The update factor $\gamma_t$ versus the iteration number for the $N=32 \times 32$
  system.}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figs/ising/N32-entropy-error-default.pdf}
  \caption{
  The average entropy error for each MC method for $N=32 \times 32$,
               $\delta_0 = 0.05\sigma$, and $T_{\min} = 1$
               as a function of number of iterations run.  The error is
               averaged over 8 independent simulations, and the best
               and worst simulations for each method are shown as a
               semi-transparent shaded area.}\label{fig:n32}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figs/ising/gamma-n128.pdf}
  \caption{
  The update factor $\gamma_t$ versus the iteration number for the $N=128 \times 128$
  system.}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figs/ising/N128-entropy-error-default.pdf}
  \caption{
  The average entropy error for each MC method for $N=128 \times 128$,
               $\delta_0 = 0.05\sigma$, and $T_{\min} = 1$
               as a function of number of iterations run.  The error is
               averaged over 8 independent simulations, and the best
               and worst simulations for each method are shown as a
               semi-transparent shaded ar.}\label{fig:n128}
\end{figure}

@@

\bibliography{ising} % Produces the bibliography via BibTeX.

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{ising/gamma-n32.pdf}
  \caption{
  The update factor $\gamma_t$ versus the iteration number for the $N=32 \times 32$
  system.}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{ising/N32-entropy-error-default.pdf}
  \caption{
  The average entropy error for each MC method for $N=32 \times 32$,
               $\delta_0 = 0.05\sigma$, and $T_{\min} = 1$
               as a function of number of iterations run.  The error is
               averaged over 8 independent simulations, and the best
               and worst simulations for each method are shown as a
               semi-transparent shaded area.}\label{fig:n32}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{ising/gamma-n128.pdf}
  \caption{
  The update factor $\gamma_t$ versus the iteration number for the $N=128 \times 128$
  system.}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{ising/N128-entropy-error-default.pdf}
  \caption{
  The average entropy error for each MC method for $N=128 \times 128$,
               $\delta_0 = 0.05\sigma$, and $T_{\min} = 1$
               as a function of number of iterations run.  The error is
               averaged over 8 independent simulations, and the best
               and worst simulations for each method are shown as a
               semi-transparent shaded ar.}\label{fig:n128}
\end{figure}

@@

\bibliography{ising/ising} % Produces the bibliography via BibTeX.
